### 2019-08-09 tramos.tex
Fixed tables, new images HD
All tables fixed

@@

\section{This work}

This thesis is an extension of the Transit Monitoring in the South project (TraMoS, see Chapter\ref{chap:tramos}) started in 2008 by Sergio Hoyer and Patricio Rojo. I selected a new sample of transiting exoplanets, all of them hot Jupiters without any companions detected to date.

>>>>

\section{Transiting Exoplanets}
The Transit method is today the most successful technique to discover extrasolar planets (see Fig.~\ref{amount_exoplanet}). The Kepler mission was launched in 2009 and during its almost nine years of provided thousands of discoveries due to this method.

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{imagenes/exo_dischist_cumulative.png}
\caption{Accumulative number of discovered exoplanets by year.}
\label{amount_exoplanet}
\end{figure}

The light curve produced by a transit event provides important information of the planetary system. For example, it is the only way on which we can derived directly the proportion between the exoplanet and star radius. It can also give information about the impact parameter, and therefore, the inclination of the orbit.

In Figure~\ref{transit} is described the architecture of a transiting exoplanet. Thanks to its geometry, the transit event as well as some parameters of the planetary system can be described with a few simple relations (cite Seager and Mallean y Winn).  When the planet passes in front of its star produced a dimming in its flux called primary transit. The maximum drop during the transit event defines the transit depth $\Delta{F}$:

\begin{equation}
    \Delta{F} = \left(\frac{R_{p}}{R_{*}}\right)^2 
\end{equation}

Where $R_{p}$ and $R_{*}$ are the planet and star radius, respectively. The numbers 1, 2, 3 and 4 correspond to the contact times: $t_{1}$, $t_{2}$, $t_{3}$ and $t_{4}$. The total duration of the transit is $t_{T} = t_{4}-t_{1}$ and the full duration is $t_{F}=t_{3}-t_{2}$. The total duration of the transit can be also described considering planetary parameters such as the period $P$, semi-major axis $a$ and orbital inclination $i$:

\begin{equation}
    t_{T} = \frac{PR_{*}}{\pi a} \sqrt{\left(1+\frac{R_{p}}{R_{*}}\right)^2-\left(\frac{a\cos i}{R_{*}}\right)}
\end{equation}

The impact parameter $b$, is the sky-projected distance between the center of the star and the planet at conjunction:

\begin{equation}
    b = \frac{a\cos{i}}{R_{*}}\left(\frac{1-e^2}{1+e\sin{\omega}}\right)
\label{impact_param}
\end{equation}

Where $\omega$ is the periastron longitude. In the case of circular orbits, the eccentricity is zero, thus Eq.~\ref{impact_param} is simplified to:

\begin{equation}
    b = \frac{a\cos{i}}{R_{*}}
\label{impact_param_simple}
\end{equation}

\begin{figure}[H]
\centering
\includegraphics[width=1.0\columnwidth]{imagenes/transit_architecture.pdf}
\caption{Architecture of a transiting exoplanet and the observed light curve. Based on the light curve itself it is possible to measure the transit depth $\Delta F$, the impact parameter $b$. From them, the planet-to-star radius ratio $R_{p}/R_{*}$ and the orbital inclination $i$ can be derived. Figure from The Handbook of Exoplanets by M. Perryman.}
\label{transit}
\end{figure}

Depending on the orbital and physical parameters of the exoplanet, the shape of the observed light curve will vary. For example, Figure \ref{transit_examples} shows how the light curve reflects the configuration of the system. Hot Jupiters are the kind of planet easier to detect, since their planet-to-star radius ratio is larger. But an smaller planet orbiting a dwarf star could produce a similar ratio of the radius. In the other hand, exoplanets with larger orbital inclinations will produce shorter drops in the flux, in comparison with planets in the same orbital-plane with the host star.

TO DO: Add studies about transmission spectroscopy.

\begin{figure}[H]
\centering
\includegraphics[width=0.8\columnwidth]{imagenes/transit_example.pdf}
\caption{Examples of transiting exoplanets and how their light curves differ between them thanks to the physical properties of the exoplanet.}
\label{transit_examples}
\end{figure}

@@
